---
title: "Module 3"
author: "Mimica"
date: "11/20/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lesson 3


## Importing and first looking the data

```{r}
getwd()
setwd('/Users/mimica/Google Drive/CodeDevelopment/Udacity/data-analysis-with-r--ud651/module3')
home_dir <- getwd()
home_dir
list.files()
pf <- read.csv("pseudo_facebook.tsv", sep = '\t')
dim(pf)
names(pf)
str(pf)
head(pf)
tail(pf)
summary(pf)
```


## Histogram of User's birthdays

```{r}
#install.packages('ggplot2')
library(ggplot2)

names(pf)
qplot(x = dob_day, data = pf)
```

## Install other themes
Run the following code in R to get other themes. 
```{r}
#install.packages('ggthemes', dependencies = TRUE)
library(ggthemes)
theme_set(theme_minimal(24))
qplot(x = dob_day, data = pf)
```

Instead of using the qplot() function, you can also use the ggplot() function to create the histogram:
```{r}
ggplot(aes(x = dob_day), data = pf) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31)
```

## Breaking into 12 histograms, one for each month of the year : Faceting

Note: The use of the scale_x_discrete() layer as shown in the video is depreciated as of ggplot2 version 2.0. You can use scale_x_continuous() instead, or use ggplot() syntax as shown below.

```{r}
qplot(x = dob_day, data = pf) +
   scale_x_continuous(breaks = 1:31) +
   facet_wrap(~dob_month, ncol = 3)
```

Equivalent ggplot syntax: 
```{r}
ggplot(data = pf, aes(x = dob_day)) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31) + 
  facet_wrap(~dob_month)
```



